---
title: "Applied ML problems"
output: html_notebook
---

```{r, include=FALSE}
rm(list=ls())
library(tidyverse)
library(reshape2)
library(tidymodels)
```

For the problem below, we will be using an extended version of the wine dataset I showed during the unsupervised ML lecture. The data is in "winemag-data_first150k_10000_processed_unscaled.csv" looks like the below. Note that I have created a host of binary variables which capture whether words or phrases appear in a critic's description of the wine.
```{r, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)
df <- readRDS("data/winemag-data_first150k_10000_processed_unscaled.rds")%>% select(-description)
kable(df[1:100, ],format="html",escape = F, col.names = colnames(df)) %>% 
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

The questions that I give are open-ended because, in developing ML algorithms, this represents what happens in reality. Nonetheless, I include a list of things that you may want to consider when building the algorithm:

1. What metrics to use to measure accuracy?
2. What is a reasonable baseline accuracy?
3. Do any features need to be created from the current set? What visualisations do I need to do to determine what these features should be?
4. Should any existing features be scaled?
5. How should I split my data into training, CV and testing sets? (I may want to use ML software's inbuilt functionality for CV.)
6. What ML methods should I try? Probably the best performing will be RFs or gradient boosted models (other than neural nets, possibly).
7. How to choose hyperparameters?


Build a model to predict the price of wine. To make the problem manageable, you may want to consider data for only the following countries: US, France, Italy, Spain, Portugal, Germany, Chile, Argentina.
